### 2019-02-14 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
I'm done for today on Chapter 4.

We refer to Section~\ref{sec:2:famousMABalgorithms} which presented two bandit algorithms, \UCB{} and Thompson Sampling,
which are both known to be efficient for stationary \emph{i.i.d.} rewards and are shown to be useful in our setting (in Section~\ref{sec:42:results}).
Then we discuss the relevance of a MAB model for our IoT application.

@@

% ----------------------------------------------------------------------
\subsection{GNU Radio implementation}
\label{sub:42:implementation}
% ----------------------------------------------------------------------

@@

The GNU Radio software provides the framework and tools to build and run software radio or just general signal-processing applications.
GNU Radio applications are a flow-graph: a series of signal processing blocks connected together to describe a data flow.
For maximum efficiency, we wrote all of our blocks in \texttt{C++}.
These flow-graphs can be written in either C++ or the Python programming language. The GNU Radio infrastructure is written entirely in C++, and many of the user tools are written in Python.
GNU Radio Companion is a graphical UI used to develop GNU Radio applications:
GRC is effectively a Python code-generation tool.
when a flow-graph is compiled in GRC, a Python code is produced, which can be executed to connect to the USRP,
create the desired GUI windows and widgets, and create and connect the blocks in the flow-graph.

@@

% ----------------------------------------------------------------------
\subsection{Numerical results}
\label{sec:42:results}
% ----------------------------------------------------------------------

>>>>

We refer to Section~\ref{sec:2:famousMABalgorithms} which presented two bandit algorithms, \UCB{} and Thompson Sampling,
which are both known to be efficient for stationary \emph{i.i.d.} rewards and are shown to be useful in our setting (in Section~\ref{sub:42:results}).
Then we discuss the relevance of a MAB model for our IoT application.

@@

% ----------------------------------------------------------------------
\subsection{Physical model and user interface of our GNU Radio implementation}
\label{sub:42:implementation}
% ----------------------------------------------------------------------

@@

The GNU Radio software provides the framework and tools to build and run software radio or just general signal-processing applications.
GNU Radio applications are a flow-graph: a series of signal processing blocks connected together to describe a data flow.
For maximum efficiency, we wrote all of our blocks in \texttt{C++}.
These flow-graphs can be written in either \texttt{C++} or the Python programming language. The GNU Radio infrastructure is written entirely in \texttt{C++}, and many of the user tools are written in Python.
GNU Radio Companion is a graphical UI used to develop GNU Radio applications:
GRC is effectively a Python code-generation tool.
when a flow-graph is compiled in GRC, a Python code is produced, which can be executed to connect to the USRP,
create the desired GUI windows and widgets, and create and connect the blocks in the flow-graph.

@@

% ----------------------------------------------------------------------
\subsection{Numerical results}
\label{sub:42:results}
% ----------------------------------------------------------------------

### 2019-02-14 2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex
I'm done for today on Chapter 4.

- Clean up notations, be sure it is OK with previous Sections

- Be sure to not repeat any motivations / maths / explanations given before

- Be sure to give enough details about the conclusions etc
}

@@

A device aims to select a channel with the highest probability of a successful transmission, for which it resorts to a reinforcement learning approach. It is formulated as MAB problem, where each channel (also called arms) is viewed as a gambling machine (bandit), and each bandit has a \emph{reward}. Then, at every trial, a device chooses a channel that maximizes the sum of the collected rewards. These \emph{rewards} are the \emph{acknowledgment} (\emph{Ack}) signals received after transmitting packets to the gateway. In this way, a successful transmission is considered when an acknowledgment is received, and a learning approach is employed to select the best channel.

We address the problem of channel selection taking into account the described Markov model for the retransmissions of end-devices. It motivates our present work for which we consider the retransmissions in the analysis of MAB algorithms. % It motivates our present work for which we consider the number of retransmissions, carried out by each device to address several MAB algorithms.

@@

We consider two hypotheses $\mathcal{H}_{1}$ and $\mathcal{H}_{2}$ defined as,
\begin{itemize}
	\item $\mathcal{H}_{1}$:
    The probability $p_{c1}$ is composed by the sum of two probabilities: i)
    the probability of colliding consecutively twice, \ie, the devices that collide at a given time slot and collide again when retransmitting their packets,
    and ii) the probability of collision related with devices that attempt to transmit in this channel for first time.
    In addition, we suppose that the number of devices that attempt to retransmit is small in comparison to the total number of devices sharing the same channel.

	\item $\mathcal{H}_{2}$:
	The total number of the back-off stages at time $t$ is constant, and it is assumed to be large enough to consider that no device will ever be in the last failure state (this case is the one on the right side in Figure~\ref{fig:43:Markov_model}), after $M$ successive failed retransmissions.
\end{itemize}

@@

As explained above, if an IoT device is experiencing a collision at the first transmission, it proceeds for the retransmission of its packet after a random back-off interval.
We denote $p_{ca}$ the probability to have a collision with a packet involved in the previous collision.
Under assumption $\mathcal{H}_{1}$, the probability that the same device's packet is experiencing again a collision at the second time slot is
\begin{equation}\label{eq:43:decomppc1}
	p_{c1} = p_{ca}+\left(1-p_{ca} \right)p_c.
\end{equation}

If the device had a collision, we consider $p_{bp}(n)$ the probability that it had a collision with \emph{exactly} $n$ packets (for any $1\leq n \leq N-1$), and that \emph{at least one} of the $n$ devices involved in the previous collision chose the same back-off interval.
Hence, under hypothesis $\mathcal{H}_{2}$, we can relate $p_{ca}$ with $p_{bp}(n)$, and the different probabilities that a device experienced a collision during the first slot and has the same back-off interval for its retransmission is,
%
\begin{equation}\label{eq:43:sumpca}
	p_{ca} = \sum_{n=1}^{N-1} p_{bp}(n).
\end{equation}

@@

Once again under $\mathcal{H}_{1}$, assuming that the number of devices involved in the first collision is small compared to $N-1$, the first terms of the sum in \eqref{eq:43:sumpc2} are predominant. Moreover, for these terms, $n$ is small compared to $N-1$, and so $N-1-n$ can be approximated to $N-1$. Thus it gives,
\begin{align}\label{eq:43:sumpca2}
	p_{ca} = & 1- \frac{1}{p_c}\sum_{n=1}^{N-1}{N-1 \choose n} x^n \left(1-x\right)^{N-1-n}\left( 1-\frac{1}{m}\right)^n,\nonumber\\
	\simeq & 1- \frac{\left(1-x\right)^{N-1}}{p_c}\sum_{n=1}^{N-1}{N-1 \choose k} x^n \left( 1-\frac{1}{m}\right)^n.
\end{align}

@@

More formally, for one device, let $N_k(t)$ be the number of times the channel $k$ (for $k\in \llbracket 1, K \rrbracket$) was selected up-to time $t-1$, for $t\geq 0$
for any $t\in\mathbb{N}$,
\begin{equation}\label{eq:43:Nkt}
	N_k(t) = \sum_{\tau=0}^{t-1} \mathbbm{1}(C(\tau) = k),
\end{equation}
where $\mathbbm{1}$ is an indicator function that is equal to $1$, if the IoT device chooses, for its $\tau$-th transmission, a channel $k$, and $0$ otherwise. The empirical mean estimator $\widehat{\mu_k}(t)$ of channel $k$ is defined as the mean reward obtained up-to time $t-1$,
\begin{equation}\label{eq:43:mukt}
	\widehat{\mu_k}(t) = \frac{1}{N_k(t)} \sum_{\tau=0}^{t-1} r_k(\tau) \mathbbm{1}(C(\tau) = k).
\end{equation}
where $r_{k}(t)$ is the reward obtained after transmission in channel $k$ at time $t$ ($1$ for a successful transmission, and $0$ otherwise)
%
A \emph{confidence} term $B_k(t)$ is given by \cite{Auer02},
\begin{equation}\label{eq:43:Bkt}
	B_k(t) = \sqrt{\alpha \log(t) / N_k(t)},
\end{equation}
where $\alpha$ refers to an exploration coefficient\footnote{~In fact, the larger this coefficient is, the longer the exploration, while the \UCB{} algorithm is proven to be order optimal for $\alpha>0.5$ \cite{Bubeck12}, and has reported a good performance for lower values of $\alpha>0$.},
that we chose equal to $1/2$, as suggested in \cite{Audibert07} and as done in previous works \cite{Bonnefoi18,Bonnefoi17}.
Then, an upper confidence bound in each channel $k$ is defined as
\begin{equation}\label{eq:43:ucb}
	U_k(t) = \widehat{\mu_k}(t) + B_k(t).
\end{equation}
Finally, the transmission channel at time step $t$
is the one maximizing this \UCB{} index $U_k(t)$,
as it is the one expected to be the best one at the current time step $t$,
\begin{equation}\label{eq:43:maxucb}
	C(t) = \arg\max_{1\leq k \leq K} U_k(t).
\end{equation}

@@

\begin{small} % XXX remove if needed
\begin{figure}[h!]
	\centering
	\begin{algorithm}[H]
		\begin{small} % XXX remove if needed
		\For(){$t = 0, \dots, T$}{
			Compute for each channel $ U_k(t) = \widehat{\mu_k}(t) + B_k(t).$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
			Transmit in channel $C(t) = \arg\max_{1\leq k \leq K} U_k(t)$\;
			Reward $r_{C(t)}(t) = 1$, if \emph{Ack} is received, else $0$\;
		}
		\caption{The \UCB{} algorithm for channel selection.}
		\label{algo:43:UCB}
		\end{small} % XXX remove if needed
	\end{algorithm}
\end{figure}
\end{small} % XXX remove if needed

@@

\vspace*{-3pt}
\begin{figure}[h!]
	\centering
	\begin{algorithm}[H]
	\begin{small} % XXX remove if needed
	\For(){$t = 0, \dots, T$}{
			\uIf{First packet transmission}{
				Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
			}
			\Else(\tcp*[f]{Random retransmission}){
				Transmit in channel $C(t) \sim \mathcal{U}(1,\ldots,K)$\;
			}
		}
		\caption{Uniform random retransmission.}    % A naive
		\label{algo:43:UCBthenRandom}
	\end{small} % XXX remove if needed
\end{algorithm}
\end{figure}

@@

\vspace*{-3pt}
\begin{small} % XXX remove if needed
\begin{figure}[h!]
	\centering
	\begin{algorithm}[H]
		\begin{small} % XXX remove if needed
		\For(){$t = 0, \dots, T$}{
			\uIf{First packet transmission}{
				Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
			}
			\Else(\tcp*[f]{Random retransmission}){
				Compute for each channel $U^r_k(t) = \widehat{\mu^r_k}(t) + B^r_k(t)$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
				Transmit in channel $C^r(t) = \arg\max_{1\leq k \leq K} U^r_k(t)$\;
				Reward $r^r_{C^r(t)}(t) = 1$, if \emph{Ack} is received, else $0$\;
			}
		}
		\caption{\UCB{} for retransmission.}    % A naive
		\label{algo:43:TwoUCB}
		\end{small} % XXX remove if needed
		\end{algorithm}
\end{figure}
\end{small} % XXX remove if needed

@@

\vspace*{-3pt}
\begin{small} % XXX remove if needed
	\begin{figure}[h!]
		\centering
		\begin{algorithm}[H]
			\begin{small} % XXX remove if needed
			% \KwData{$\forall k,j\in[\![1;K]\!]$, $N_k^j(t)$, $\widehat{\mu_k}^j(t)$, $B_k^j(t)$ and $U_k^j(t)$}
			\For(\tcp*[f]{At every time step})
			{$t = 0, \dots, T$}{
				\uIf{First packet transmission}{
					Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
				}
				\Else(\tcp*[f]{Packet retransmission}){ % Retr. after trying channel $j$
					j $\leftarrow$ last channel selected by first-stage \UCB\;
					Compute for each channel $U_k^j(t) = \widehat{\mu_k}^j(t) + B_k^j(t)$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
					Transmit in channel $C^j(t) = \arg\max_{1\leq k \leq K} U^j_k(t)$\;
					Reward $r^j_{C^j(t)}(t) = 1$ if \emph{Ack} is received, else $0$\;
				}
			}
			\caption{$K$ different {\UCB}s for retransmission.}
			\label{algo:43:UCBthenKp1}
			\end{small} % XXX remove if needed
		\end{algorithm}
	\end{figure}
\end{small} % XXX remove if needed

@@

\vspace*{-3pt}
\begin{small} % XXX remove if needed
	\begin{figure}[h!]
		\centering
		\begin{algorithm}[H]
			\begin{small} % XXX remove if needed
			\For(\tcp*[f]{At every time step})
			{$t = 0, \dots, T$}{
				\uIf{First packet transmission}{
			 		Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
				}
				\uElseIf(\tcp*[f]{Random selection}){$t \leq \Delta$}{
					Transmit randomly in a channel $C(t) \sim \mathcal{U}(1,\ldots,K)$.
				}
				\Else(\tcp*[f]{Delayed \UCB{}}){
					Compute for each channel $ U^d_k(t) = \widehat{\mu^d_k}(t) + B^d_k(t)$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
					Transmit in channel $C^d(t) = \arg\max_{1\leq k \leq K} U^d_k(t)$\;
					Reward $r^d_{C^d(t)}(t) = 1$ if \emph{Ack} is received, else $0$\;
				}
			}
			\caption{Delayed \UCB{} for retransmission.}
			\label{algo:43:UCBwithDelay}
			\end{small} % XXX remove if needed
		\end{algorithm}
	\end{figure}
\end{small} % XXX remove if needed

>>>>

- Be sure to not repeat any motivations / maths / explanations given before
}

@@

A device aims to select a channel with the highest probability of a successful transmission, for which it resorts to a reinforcement learning approach. It is formulated as MAB problem, where each channel (also called arms) is viewed as a gambling machine (bandit), and each bandit has a \emph{reward}. Then, at every trial, a device chooses a channel that maximizes the sum of the collected rewards. These \emph{rewards} are the \emph{acknowledgment} (\emph{Ack}) signals received after transmitting packets to the gateway. In this way, a transmission is considered successful when an acknowledgment is received, and a learning approach is employed to select the best channel.

We address the problem of channel selection taking into account the described Markov model for the retransmissions of end-devices.
% It motivates our present work for which we consider the retransmissions in the analysis of MAB algorithms.
It motivates our present work for which we consider the number of retransmissions, carried out by each device to address several MAB algorithms.

@@

We consider two hypotheses $\cH_{1}$ and $\cH_{2}$ defined as,
\begin{itemize}
	\item $\cH_{1}$:
    The probability $p_{c1}$ is composed by the sum of two probabilities: i)
    the probability of colliding consecutively twice, \ie, the devices that collide at a given time slot and collide again when retransmitting their packets,
    and ii) the probability of collision related with devices that attempt to transmit in this channel for first time.
    In addition, we suppose that the number of devices that attempt to retransmit is small in comparison to the total number of devices sharing the same channel.

	\item $\cH_{2}$:
	The total number of the back-off stages at time $t$ is constant, and it is assumed to be large enough to consider that no device will ever be in the last failure state (this case is the one on the right side in Figure~\ref{fig:43:Markov_model}), after $M$ successive failed retransmissions.
\end{itemize}

@@

As explained above, if an IoT device is experiencing a collision at the first transmission, it proceeds for the retransmission of its packet after a random back-off interval.
We denote $p_{ca}$ the probability to have a collision with a packet involved in the previous collision.
Under assumption $\cH_{1}$, the probability that the same device's packet is experiencing again a collision at the second time slot is
\begin{equation}\label{eq:43:decomppc1}
	p_{c1} = p_{ca}+\left(1-p_{ca} \right)p_c.
\end{equation}

If the device had a collision, we consider $p_{bp}(n)$ the probability that it had a collision with \emph{exactly} $n$ packets (for any $1\leq n \leq N-1$), and that \emph{at least one} of the $n$ devices involved in the previous collision chose the same back-off interval.
Hence, under hypothesis $\cH_{2}$, we can relate $p_{ca}$ with $p_{bp}(n)$, and the different probabilities that a device experienced a collision during the first slot and has the same back-off interval for its retransmission is,
%
\begin{equation}\label{eq:43:sumpca}
	p_{ca} = \sum_{n=1}^{N-1} p_{bp}(n).
\end{equation}

@@

Once again under $\cH_{1}$, assuming that the number of devices involved in the first collision is small compared to $N-1$, the first terms of the sum in \eqref{eq:43:sumpc2} are predominant. Moreover, for these terms, $n$ is small compared to $N-1$, and so $N-1-n$ can be approximated to $N-1$. Thus it gives,
\begin{align}\label{eq:43:sumpca2}
	p_{ca} = & 1- \frac{1}{p_c}\sum_{n=1}^{N-1}{N-1 \choose n} x^n \left(1-x\right)^{N-1-n}\left( 1-\frac{1}{m}\right)^n,\nonumber\\
	\simeq & 1- \frac{\left(1-x\right)^{N-1}}{p_c}\sum_{n=1}^{N-1}{N-1 \choose k} x^n \left( 1-\frac{1}{m}\right)^n.
\end{align}

@@

More formally, for one device, let $N_k(t)$ be the number of times the channel $k$ (for $k\in \llbracket 1, K \rrbracket$) was selected up-to time $t-1$, for $t\geq 0$
for any $t\in\mathbb{N}$,
\begin{equation}\label{eq:43:Nkt}
	N_k(t) = \sum_{\tau=0}^{t-1} \mathbbm{1}(C(\tau) = k),
\end{equation}
The empirical mean estimator $\widehat{\mu_k}(t)$ of channel $k$ is defined as the mean reward obtained up-to time $t-1$,
\begin{equation}\label{eq:43:mukt}
	\widehat{\mu_k}(t) = \frac{1}{N_k(t)} \sum_{\tau=0}^{t-1} r_k(\tau) \mathbbm{1}(C(\tau) = k).
\end{equation}
where $r_{k}(t)$ is the reward obtained after transmission in channel $k$ at time $t$ ($1$ for a successful transmission, and $0$ otherwise)
%
A \emph{confidence} term $B_k(t)$ is given by \cite{Auer02},
\begin{equation}\label{eq:43:Bkt}
	B_k(t) = \sqrt{\alpha \log(t) / N_k(t)},
\end{equation}
where $\alpha$ refers to an exploration coefficient,
% \footnote{~In fact, the larger this coefficient is, the longer the exploration, while the \UCB{} algorithm is proven to be order optimal for $\alpha>0.5$ \cite{Bubeck12}, and has reported a good performance for lower values of $\alpha>0$.},
that we chose equal to $1/2$, as suggested in \cite{Audibert07} and as done in previous works \cite{Bonnefoi18,Bonnefoi17}.
Then, an upper confidence bound in each channel $k$ is defined as
\begin{equation}\label{eq:43:ucb}
	U_k(t) = \widehat{\mu_k}(t) + B_k(t).
\end{equation}
Finally, the transmission channel at time step $t$
is the one maximizing this \UCB{} index $U_k(t)$,
as it is the one expected to be the best one at the current time step $t$,
\begin{equation}\label{eq:43:maxucb}
	C(t) = \arg\max_{1\leq k \leq K} U_k(t).
\end{equation}

@@

% \begin{small} % XXX remove if needed
\begin{figure}[h!]
	\centering
	\begin{algorithm}[H]
		% \begin{small} % XXX remove if needed
		\For(){$t = 0, \dots, T$}{
			Compute for each channel $ U_k(t) = \widehat{\mu_k}(t) + B_k(t)$, following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
			Transmit in channel $C(t) = \arg\max_{1\leq k \leq K} U_k(t)$\;
			Reward $r_{C(t)}(t) = 1$, if \emph{Ack} is received, else $0$\;
		}
		\caption{The \UCB{} algorithm for channel selection.}
		\label{algo:43:UCB}
		% \end{small} % XXX remove if needed
	\end{algorithm}
\end{figure}
% \end{small} % XXX remove if needed

@@

\vspace*{-3pt}
\begin{figure}[h!]
	\centering
	\begin{algorithm}[H]
	% \begin{small} % XXX remove if needed
	\For(){$t = 0, \dots, T$}{
			\uIf{First packet transmission}{
				Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
			}
			\Else(\tcp*[f]{Random retransmission}){
				Transmit in channel $C(t) \sim \mathcal{U}(1,\ldots,K)$\;
			}
		}
		\caption{Uniform random retransmission.}    % A naive
		\label{algo:43:UCBthenRandom}
	% \end{small} % XXX remove if needed
\end{algorithm}
\end{figure}

@@

\vspace*{-3pt}
% \begin{small} % XXX remove if needed
\begin{figure}[h!]
	\centering
	\begin{algorithm}[H]
		% \begin{small} % XXX remove if needed
		\For(){$t = 0, \dots, T$}{
			\uIf{First packet transmission}{
				Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
			}
			\Else(\tcp*[f]{Packet retransmission}){
				Compute for each channel $U^r_k(t) = \widehat{\mu^r_k}(t) + B^r_k(t)$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
				Transmit in channel $C^r(t) = \arg\max_{1\leq k \leq K} U^r_k(t)$\;
				Reward $r^r_{C^r(t)}(t) = 1$, if \emph{Ack} is received, else $0$\;
			}
		}
		\caption{\UCB{} for retransmission.}    % A naive
		\label{algo:43:TwoUCB}
		% \end{small} % XXX remove if needed
		\end{algorithm}
\end{figure}
% \end{small} % XXX remove if needed

@@

\vspace*{-3pt}
% \begin{small} % XXX remove if needed
	\begin{figure}[h!]
		\centering
		\begin{algorithm}[H]
			% \begin{small} % XXX remove if needed
			% \KwData{$\forall k,j\in[\![1;K]\!]$, $N_k^j(t)$, $\widehat{\mu_k}^j(t)$, $B_k^j(t)$ and $U_k^j(t)$}
			\For(\tcp*[f]{At every time step})
			{$t = 0, \dots, T$}{
				\uIf{First packet transmission}{
					Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
				}
				\Else(\tcp*[f]{Packet retransmission}){ % Retr. after trying channel $j$
					j $\leftarrow$ last channel selected by first-stage \UCB\;
					Compute for each channel $U_k^j(t) = \widehat{\mu_k}^j(t) + B_k^j(t)$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
					Transmit in channel $C^j(t) = \arg\max_{1\leq k \leq K} U^j_k(t)$\;
					Reward $r^j_{C^j(t)}(t) = 1$ if \emph{Ack} is received, else $0$\;
				}
			}
			\caption{$K$ different {\UCB}s for retransmission.}
			\label{algo:43:UCBthenKp1}
			% \end{small} % XXX remove if needed
		\end{algorithm}
	\end{figure}
% \end{small} % XXX remove if needed

@@

\vspace*{-3pt}
% \begin{small} % XXX remove if needed
	\begin{figure}[h!]
		\centering
		\begin{algorithm}[H]
			% \begin{small} % XXX remove if needed
			\For(\tcp*[f]{At every time step})
			{$t = 0, \dots, T$}{
				\uIf{First packet transmission}{
			 		Use first-stage \UCB. %as in Algorithm~\ref{algo:43:UCB}.
				}
				\uElseIf(\tcp*[f]{Random retransmission}){$t \leq \Delta$}{
					Transmit randomly in a channel $C(t) \sim \mathcal{U}(1,\ldots,K)$.
				}
				\Else(\tcp*[f]{Delayed \UCB{}}){
					Compute for each channel $ U^d_k(t) = \widehat{\mu^d_k}(t) + B^d_k(t)$ following Eqs.~\eqref{eq:43:Nkt},~\eqref{eq:43:mukt}, and~\eqref{eq:43:Bkt}\;
					Transmit in channel $C^d(t) = \arg\max_{1\leq k \leq K} U^d_k(t)$\;
					Reward $r^d_{C^d(t)}(t) = 1$ if \emph{Ack} is received, else $0$\;
				}
			}
			\caption{Delayed \UCB{} for retransmission.}
			\label{algo:43:UCBwithDelay}
			% \end{small} % XXX remove if needed
		\end{algorithm}
	\end{figure}
% \end{small} % XXX remove if needed

### 2019-02-14 2-Chapters/4-Chapter/chapter4.tex
I'm done for today on Chapter 4.

This is both a surprising and a very encouraging result, showing that application of bandit algorithms tailored for a stochastic model is still useful in broader settings.
The fully \emph{decentralized} application of classic stochastic MAB algorithms are almost as efficient as the best possible centralized policy in this setting, after a short learning period, even though the dynamic devices \emph{can not} communicate with each others, and \emph{do not} know the system parameters.
We will investigate this behavior in order to understand it better theoretically.
We will also experiment more with adversarial algorithms, to confirm that they work less efficiently than stochastic bandit algorithms in our non-stochastic setting.

@@

Another extension could be to not have a Bernoulli process (or any random process), but a fixed rate of transmission, \emph{e.g.}, one transmission a day.
So additionally to deciding the channel for communication, each device has to also decide when to communicate.
This is another direction of research, that we will investigate in the future.

@@

% ----------------------------------------------------------------------------
\section{Appendix for Chapter~\ref{chapter:4}}
\label{sec:4:appendix}
% ----------------------------------------------------------------------------

>>>>

This is both a surprising and a very encouraging result, showing that application of bandit algorithms tailored for a stochastic model is still useful in broader settings.
The fully \emph{decentralized} application of classic stochastic MAB algorithms are almost as efficient as the best possible centralized policy in this setting, after a short learning period, even though the dynamic devices \emph{can not} communicate with each others, and \emph{do not} know the system parameters.

@@

Another extension could be to not have a Bernoulli process (or any random process), but a fixed rate of transmission, \emph{e.g.}, one transmission a day.
So additionally to deciding the channel for communication, each device has to also decide when to communicate.
% This is another direction of research, that we will investigate in the future.

% We will investigate this behavior in order to understand it better theoretically.
% We will also experiment more with adversarial algorithms, to confirm that they work less efficiently than stochastic bandit algorithms in our non-stochastic setting.

@@

\newpage
% ----------------------------------------------------------------------------
\section{Appendix for Chapter~\ref{chapter:4}}
\label{sec:4:appendix}
% ----------------------------------------------------------------------------
